\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 3 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

As demonstrated by \citet{habermann_1960}, mobility ratio (MR, see Section~\ref{section:intro}) is a key-parameter to assess the efficiency during fluid displacement, and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
\begin{equation}
 \text{MR} \; = \frac{\mathcal{K}_{ri} \; \mu_{j}}{\mathcal{K}_{rj} \; \mu_{i}}. 
\label{eq:MR}
\end{equation}
MR is a function not only of fluid viscosities and saturations, but also the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.

>>>>

As demonstrated by \citet{habermann_1960}, mobility ratio (MR, see Section~\ref{section:intro}) is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
\begin{equation}
 \text{MR} \; = \frac{\mathcal{K}_{ri} \; \mu_{j}}{\mathcal{K}_{rj} \; \mu_{i}}. 
\label{eq:MR}
\end{equation}
MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
